Analysis of Open Data and Computational Reproducibility in Registered Reports in Psychology

### 2019-05-22 reproducing_registered_reports.Rmd
updated manuscript

library(readxl)
library(here)
library(irr)
library(codebook)

all_data <- read_excel("Data_for_Analysis_of_Open_Data_and_Computational_Reproducibility_in_Registered_Reports_in_Psychology.xlsx", n_max = 62)
codebook_data <- read_excel("Data_for_Analysis_of_Open_Data_and_Computational_Reproducibility_in_Registered_Reports_in_Psychology.xlsx", sheet = "Codebook")

#Use the codebook package to add labels to variables
var_label(all_data) <- dict_to_list(codebook_data)

@@

Researchers are currently exploring ways to make science more open and transparent. Among novel developments such as pre-registration, pre-prints, and open peer review, an increasing number of journals, funders, and researchers are beginning to expect that data, materials, and analysis code will be shared by default with scientific publications (e.g., [@morey_peer_2016]. Sharing data and analysis code with scientific publications allows others to more easily reproduce, check, and build on existing work. However, since most researchers have received limited training in how to share data and code to facilitate reproducible science, it is important to evaluate how data and code are currently being shared to learn what needs to be improved. With this goal in mind, we aimed to computationally reproduce the results of Registered Reports published in the psychological literature.

It is desirable that research is reproducible. Data availability has the potential to save time in the long run by facilitating the re-use of data, allows findings to be more easily included in meta-analyses, and makes it possible for peers to check and correct published findings. According to @kitzes_practice_2017, computational reproducibility means that ”a second investigator (including the original researcher in the future) can recreate the final reported results of the project, including key quantitative findings, tables, and figures, given only a set of files and written instructions.” For scientific research to be computationally reproducible, the data and code needs to be shared. However, the availability of data and code in itself is not enough. These materials also need to be linked in the article so that readers know where to find them. Preferably, the data should be available in a format that can be read by open source software. Having access to rdata and analysis files is not worth much of these files can not be understood. Variables must be described and labeled (e.g., in a codebook), and code should be annotated. Finally, the results reported in the scientific manuscript should be reproducible, which means the data and code can be used to compute the results that are reported in the published article.

Recently, scholars have started to empirically examine the extent to which data is shared with published articles, and, if so, whether it was possible to reproduce the data analysis reported in the published article. @hardwicke_data_2018 examined the reproducibility of 35 articles published in the journal Cognition. Eleven  articles could be reproduced without assistance from the original authors, and 13 articles contained at least one outcome that could not be reproduced even with author assistance. Hardwicke et al. (2018) estimated that it took between 2-4 hours to reproduce a paper, but they did not record the exact time. @stockemer_data_2018 analyzed reproducibility in all articles published in 2015 in three political science journals. They emailed authors for the code and data, and found that for 71 articles for which they received code and data, one could not be reproduced due to a lack of a software license, and 16 articles could not be reproduced with access to the required software. For the remaining articles, 32 could be exactly reproduced, 19 could be reproduced with slight differences, and 3 articles yielded significantly different results. @stodden_empirical_2018 analyzed data availability in the journal science in 2011-2012 and found that 26 of 204 (or 13%) of articles provided information to retrieve data and/or code without contacting the authors. For all datasets they acquired after e-mailing authors for data and code, 26% was estimated to be computationally reproducible. It seems there is clear room for improvement in how reproducible published articles are.

We set out to examine the data availability and reproducibility in Registered Reports published in psychological science. Our main interest is to examine whether data and code authors shared with their paper were reusable without contacting the original authors. The benefit of sharing data and code over making them available upon request is that even if the original author can no longer be reached, the data is still reusable. Registered Reports are a relatively novel development in psychology. Before data collection commences, the introduction and methods are peer-reviewed, after whichauthors can receive an 'in principle acceptance'. This means the article will be published as long as the authors follow their preregistered data collection and analysis plan [@chambers_instead_2014; @nosek_registered_2014]. The population of Registered Reports in psychology is still relatively small (91 Registered Reports had been published as of February 22, 2018), which makes it possible to examine it in full. 
The novelty of Registered Reports may attract early adopters who are also exploring other novel developments in psychology, such as sharing data and code. We assumed that researchers who publish Registered Reports would also be likely to share data and code in public repositories. In line with our assumptions, `r sum(all_data$availability, na.rm = TRUE)` out of `r length(all_data$doi)` articles in our final dataset shared data and code (`r round(100*sum(all_data$availability, na.rm = TRUE)/length(all_data$doi),1)`%). In comparison, after *Cognition* introduced a mandatory data sharing policy, 136 out of 174 articles (78.2%) had a data availability statement, and 49% of 174 articles had reusable data (Hardwicke et al., 2018). Sharing analysis code was not required, and only 18 out of 174 articles provided the analysis code (10.3%). To evaluate the reproducibility of findings published in Registered Reports, we examine if data can be located, are available at the indicated location, can be opened in open-source software, are understandable, and can be used to reproduce the reported results.

@@

Our main objective was to examine how reusable data and code underlying Registered Reports are, based purely on the information provided in the published literature. We examined the extent to which we could reproduce reported analyses without contacting the original authors. While reproducing the results reported in Registered Reports, we kept track of factors that facilitated reproducibility or that made reproducing the result more difficult. We report these qualitative findings with an aim to highlight how current practices can be improved.

@@

To find Registered Reports published in psychology, we drew from a database of registered reports maintained by by Center for Open Science. At the start of this project (06-05-2018) this database consisted of 118 published Registered Reports. Eighty-one articles in this database were published in the psychological literature. We limited our analysis to studies performed by single groups, since such papers are most representative of the psychological literature, and excluded 7 large scale collaborations where dedicated team members worked on making the analysis reproducible, such as Registered Replication Reports [@hagger_multilab_2016] and Many Labs projects [@klein_investigating_2014; @klein_many_2018]. Upon further inspection of the 72 papers left in the dataset, it turned out that 10 were not formally Registered Reports. This left `r length(all_data$doi)` studies in our sample. When evaluating whether we could reproduce the original results, we limited ourselves to statistical software packages that we had experience with (R, SPSS, and JASP) and excluded studies that required expertise in software packages we are not trained in (e.g., dedicated EEG software, Python, Matlab), which led to the exclusion of `r sum(all_data$included_language == FALSE, na.rm = TRUE)` additional studies.

@@

We set out to reproduce the `r length(all_data$doi)` papers that met our inclusion criteria. For each article we coded whether the data and code were (a) linked, (b) available, (c) not software-specific, (d) understandable, and (e) reproducible. These five categories were inspired by FAIR data principles [@wilkinson_fair_2016] that address the findability, accessibility, interoperability, and reusability of data and code, but we did not explicitly code whether papers adhered to the exact definitions of the four FAIR principles. Our main aim was to examine the reproducibility of results, while adhering to FAIR criteria requires meeting more stringent requirements, for example concerning the presence of meta-data (which is missing for practically all datasets). We considered data and code to be linked when the manuscript included a unique link to the data and scripts. Ideally, such a link consists of a stable digital object identifier (DOI). A hyperlink to a website that contains the data and script also suffices, although such regular links are known to often break over time [@gertler_reference_2017].

Of the `r length(all_data$doi)` papers, `r sum(all_data$linked)` had data and/or code that was linked to the article. Linking to data does not mean the data is actually available, and not linking to data in an article does not mean data is unavailable. For one article the link no longer worked (highlighting the need to use a stable DOI when linking to data). For three articles the link still worked, but there was no data at the linked destination. For three articles where there was no link to the data in the article, we were nevertheless able to find data on the Open Science Framework when searching for the title of the paper. For one paper the data was linked but not available, as the data was embargoed until a future date. Altogether, data was available for `r sum(all_data$availability)` out of `r length(all_data$doi)` papers.

We also coded the extent to which data and code was specific to software that was not freely available. When open source software is used, the analyses can be reproduced by anyone with a computer and internet, regardless of whether they have bought the same software package. When proprietary software is used, results might still be reproducible by anyone, but it could require more effort to do so. For example, SPSS produces proprietary .sav and .sps files. However, .sav files can be opened in R, and .sps files can be opened by a text editor and the code can be rewritten, as long the code is annotated well enough to be recoded into R. Note that we had access to SPSS and therefore reproduced the analyses using the original .sps scripts where available. The data files of one article where an EEG study was reported consisted of .eeg, .vhdr, and vmrk files that were analyzed in matlab, which we could not reproduce using open source software. This left `r sum(all_data$not_software_specific, na.rm = TRUE)` papers (see Figure 1).

@@

\caption{Of all articles in the Registered Report database 79 were psychology related, and `r length(all_data$doi)` were registered reports not part of a multi-lab Registered Replication Report. Of these `r length(all_data$doi)` papers, `r sum(all_data$linked)` linked to the data. After searching the OSF, data was available for `r sum(all_data$availability)` studies. Of these datasets, `r sum(all_data$understandable, na.rm = TRUE)` were labelled well enough so that it was clear what variables meant. Of the `r length(all_data$doi)` papers `r sum(all_data$analysis_script_included, na.rm = TRUE)` shared the analysis script and data, for which `r spss_or_r_or_jasp` were in SPSS, R or JASP. Of these, the analysis script could be run for `r sum(all_data$run_script_final, na.rm = TRUE)`, of which `r sum(all_data$reproducible_final, na.rm = TRUE)` reproduced all main results. 
}

@@

One of the reasons to share data is allow other researchers to reproduce the reported results. Another important reason to share data is to enable other researchers to reuse the data. If the data can be understood by others, they can be used to answer novel research questions. This is one of the reasons why it is recommended to describe the dataset variables in a codebook. If the variables are not clearly described (e.g., the dataset consists of variables identified by abbreviations that only make sense to the original researcher), other researchers will not be able to reuse the data to answer novel questions. In our analyses, data were scored as 'understandable' when all variables were clearly named (e.g., 'Condition') and the values for variables were labeled (e.g., 0 = control, 1 = experimental). Out of the `r sum(all_data$not_software_specific, na.rm = TRUE)` papers with available data in a format that was not software specific, only `r sum(all_data$understandable, na.rm = TRUE)` datasets were described in enough detail to be understandable. This highlights the importance of adding a codebook with a datafile.

Finally, we examined how many of the `r sum(all_data$not_software_specific, na.rm = TRUE)` non-software-specific papers could be reproduced. It is possible that running the code on the data reproduces all analyses, even when the data file itself is not understandable (i.e., the data columns are not labeled). Two authors coded SPSS, R, and JASP analyses regarding (a) the executability of the script, and (b) the reproducibility of the results. After the initial coding, inter-rater reliability was low (`r agree(cbind(all_data$run_script_po == FALSE, all_data$run_script_jg == FALSE))$value`% agreement on executability, and `r agree(cbind(all_data$reproducible_po == FALSE, all_data$reproducible_jg == FALSE))$value`% agreement on reproducibility for SPSS scripts, `r agree(cbind(all_data$run_script_po == FALSE, all_data$run_script_nc == FALSE))$value`% agreement on executability, and `r agree(cbind(all_data$reproducible_po == FALSE, all_data$reproducible_nc == FALSE))$value`% agreement on reproducibility for R scripts). This initial low agreement provided two important insights about the definition of reproducibility and executability on the one hand, and the role of expertise on the other hand.

We used a dichotomous coding scheme to when coding whether the script could be executed whether the results could be reproduced ('yes' or 'no'). Code often needed minor adjustments to run on the data, such as changing file locations, or loading packages in R, and coders sometimes took different approaches to how much they would adjust the code to make it run on the data. Furthermore, coders initially used different thresholds of reproducibility, based on whether every single result reported in a paper could be reproduced by the code and data, or only the main results reported in the article. After evaluating our initial coding round, we considered an article reproducible if we could get the same main results as represented in the paper with at best minor changes to make the scripts run on the data. This means we considered the analysis reproducible, even if variables could only be found with reasonable effort or by making assumptions about how variable names mapped onto variables reported in the data analysis. Furthermore, we changed folder locations when needed and loaded libraries that were required. Finally, even though sometimes Figures contained relevant information (e.g., the pattern of means) we did not require all figures to be reproducible.

@@

All authors have collectively discussed the discording ratings, which on several occasions led to clarifying ambiguities in rating strategies and correcting mistakes in the process of paper analysis (e.g. overlooked script files). The final ratings presented here have been discussed and approved by all authors, but will likely not be completely flawless, as different teams of coders will likely reach slightly different conclusions (i.e., perfect reliability would be extremely difficult to achieve). It should be noted that the main goal of our analysis is to evaluate whether there is room for improvement, and how the reproducibility of results can be improved in practice. We expect any estimate of the reproducibility of results to improve over time as the field develops better standards and researchers are trained in reproducibility.

For each article two coders examined whether the code could be run on the data. Of the original `r length(all_data$doi)` articles, `r sum(all_data$included_language == FALSE, na.rm = TRUE, na.rm = TRUE)` used Matlab and Python and were excluded from the analysis due to a lack of expertise in our team with these languages. In total code and data were available for `r sum(all_data$analysis_script_included ==TRUE & all_data$availability == TRUE, na.rm = TRUE)` articles, of which `r sum(all_data$analysis_script_included ==TRUE & all_data$availability == TRUE & all_data$included_language ==TRUE, na.rm = TRUE)` used R, SPSS, or JASP. We were able to run the code for `r sum(all_data$run_script_final == TRUE, na.rm = TRUE)` out of the `r sum(all_data$analysis_script_included ==TRUE & all_data$availability == TRUE & all_data$included_language ==TRUE, na.rm = TRUE)` articles that used SPSS, R, and JASP. R was used as a coding language in `r length(run_script_r)`, of which `r sum(run_script_r)` scripts could be run on the data, `r length(run_script_spss)` papers used SPSS, for `r sum(run_script_spss)` of which the script could be run, and `r length(run_script_r_spss)` papers used both SPSS and R, for which the scripts could be run for all `r sum(run_script_r_spss)` papers. JASP does not seperate the data and code, but instead stores both in a single JASP file. This means that the analyses are always directly linked to the code for every output, you can see which settings were used to generate it, as well as the data that were used. Because of this useful feature, because the JASP files were available for the `r sum(run_script_jasp)` articles that relied on JASP for the analyses, we could always see how the output was generated.

@@

We analyzed data and scripts of `r length(all_data$doi)` Registered Reports to examine how many authors shared their data and code, and how often main results reported in the manuscript could be reproduced. In total, `r sum(all_data$analysis_script_included ==TRUE & all_data$availability == TRUE, na.rm = TRUE)` out of `r length(all_data$doi)` (or `r round(100*sum(all_data$analysis_script_included ==TRUE & all_data$availability == TRUE, na.rm = TRUE)/length(all_data$doi),1)`%) of the articles shared the underlying data and the code that was used to generate the results. Of the papers that shared both the data and the analysis code and used software we had experience with, we could reproduce the main results for approximately half the papers. Authors of Registered Reports in psychology seem to voluntarily choose to share data and code relatively often compared to authors of articles in political science [@stockemer_data_2018]. Compared to authors of non-registered reports in psychology, voluntary data and code sharing is relatively high, as is the reproducibility rate (taking into account that we reproduced articles without contacting the original authors). The reproducibility rate was higher than the 31% rate observed by Hardwicke et al. (2018), and both voluntary data sharing as reproducibility were higher than in the sample of papers from the journal Science in 2011-2012 analyzing in @stodden_empirical_2018.

Nevertheless, the reproducibility rate for articles where data and code were available show there is clear room for improvement in how reproducible published Registered Reports are, when we attempted to reproduce main analyses without contacting the authors. One of the main goals of our project was to identify ways to improve the reproducibility of published articles. We encountered several common issues that made results reported in Registered Reports difficult to reproduce (cf. Hardwicke et al., 2018). This leads to X points researchers in psychology should focus on to improve reproducibility, namely (a) add a codebook to data files, (b) annotate code so it is clear what the code does, and clearly structure code (e.g., using a README) so others know which output anaysis code creates, (c) list packages that are required in R and the versions used at the top of your R file, (d) check whether the code you shared still reproduces all analyses after revisions during the peer review process. We will discuss each of these points below, and link to examples of good practices that we encountered.

@@

Second, code should be well-annotated, so that it is understandable for researchers who did not write the code. Well-annotated code makes clear what the analysis code does, in which order it should be run, and which output each section of analysis code generates. A good example of well-annotated code can be found in the materials of @weston_role_2018. It helps to make clear how the analysis code relates to the analyses reported in the paper, to make it easier for others to identify which code generates which results in the paper. For one manuscript which was coded as not reproducible, there was too much unstructured code, and each analyses took too long to run, that it was decided that the manuscript was not reproducible with a reasonable amount of effort mainly due to the lack of a clear indication which code needed to be run to reproduce specific results. Explicitly linking code in the analysis script to the final manuscript also helps researchers to check whether all results in the article are reproduced by the shared code. An example of a data analysis file that clearly links the code to the final articles can be found in the materials of @voorspoels_can_2014. If analyses are performed that are not included in the manuscript, this should be stated explicitly (e.g., assumption checks, exploratory analyses, etc.). The structure of analysis scripts can often be improved by creating different sections in the code, or creating different files for different parts of the data analysis (e.g., data cleaning, data preparation, exploratory data analysis, and confirmatory data analysis scripts). It is also highly recommended to perform a final check after the peer-review process has been completed to make sure any changes in the code introduced during the peer-review process are reflected in the shared data and code.

@@

While trying to reproduce the results of SPSS scripts, the biggest issue was the often confusing and unclear structure of the scripts. Large portion of the scripts were not annotated, and it was unclear which results they should produce. Often, the descriptive, confirmatory and exploratory analyses were not easily distinguishable because of an overall lack of structure. The absence of understandable variable and value labels in more than half of all SPSS scripts hindered our attempts to reproduce these results. Often the only time-efficient way to check if an article was reproducible so was to run the whole script, and search try to identify specific p-values or effect sizes from the article in the SPSS output. SPSS users should take greater care to clearly organize their analysis scripts by adding comments or a README file that links results generated by the SPSS script to the analyses reported in the manuscript. Another frequent problem consisted of missing or incorrectly labeled variables in the dataset, so the script could not run properly. We expect this is the result of authors updating or modifying either their datasets or their scripts during the publication process. This issue could be easily detected if a second author of the manuscript attempted to reproduce the analyses reported in the final manuscript before the data and scripts are shared publicly.

>>>>

library(readxl)
library(here)
library(irr)

all_data <- read_excel("Data_for_Analysis_of_Open_Data_and_Computational_Reproducibility_in_Registered_Reports_in_Psychology.xlsx", n_max = 62)

@@

Researchers are currently exploring ways to make science more open and transparent. Among novel developments such as pre-registration, pre-prints, and open peer review, an increasing number of journals, funders, and researchers are beginning to expect that data, materials, and analysis code will be shared by default with scientific publications (e.g., [@morey_peer_2016]. Sharing data and analysis code with scientific publications allows others to more easily reproduce, check, and build on existing work. This requires the development of new skills and best practices, since most scientists have not received training in how to make their work reproducible. It is important to evaluate how data and code are currently being shared, and how easy it is to reproduce analyses reported in the published literature, to learn what can be improved. With this goal in mind, we computationally reproduced the main results of Registered Reports published in the psychological literature.

It is desirable that research is reproducible. Data availability has the potential to make science more efficient by facilitating the re-use of data. The availability of analysis code makes it possible for peers to check and correct published findings. According to @kitzes_practice_2017, computational reproducibility means that ”a second investigator (including the original researcher in the future) can recreate the final reported results of the project, including key quantitative findings, tables, and figures, given only a set of files and written instructions.” For scientific research to be computationally reproducible, the data and code needs to be shared.

However, the availability of data and code in itself is not enough. Articles need to link to these materials so that readers know where to find them. Preferably, the data should be available in a format that can be read by open source software. Variables must be described and labeled (e.g., in a codebook), and code should be annotated. Finally, the results reported in the scientific manuscript should be reproducible, which means the data and code can be used to compute the results that are reported in the published article.

Recently, scholars have started to empirically examine the extent to which data is shared with published articles, and, if so, whether it was possible to reproduce the data analysis reported in the published article. @hardwicke_data_2018 examined the reproducibility of 35 articles published in the journal *Cognition*. Eleven  articles could be reproduced without assistance from the original authors, and 13 articles contained at least one outcome that could not be reproduced even with author assistance. Hardwicke et al. (2018) estimated that it took between 2-4 hours to reproduce the reported results, but they did not record the exact time. @stockemer_data_2018 analyzed reproducibility in all articles published in 2015 in three political science journals. They emailed authors for the code and data, and found that for 71 articles for which they received code and data, one could not be reproduced due to a lack of a software license, and 16 articles could not be reproduced with access to the required software. For the remaining articles, 32 could be exactly reproduced, 19 could be reproduced with slight differences, and 3 articles yielded significantly different results. @stodden_empirical_2018 analyzed data availability in the journal *Science* in 2011-2012 and found that 26 of 204 (or 13%) of articles provided information to retrieve data and/or code without contacting the authors. For all datasets they acquired after e-mailing authors for data and code, 26% was estimated to be computationally reproducible. These studies reveal that there is clear room for improvement in how reproducible published articles are.

We set out to examine the data availability and reproducibility in Registered Reports published in psychological science. Our main interest was to examine the computational reproducibility of the main analyses reported in published articles, without contacting the original authors. One of the main benefits of sharing data and code with the article (compared to making these files available upon request) is that results can be reproduced, and data reused even if the original author can no longer be reached. Registered Reports are a novel development in psychology. Before data collection commences, the introduction and methods are peer-reviewed, after which authors can receive an 'in principle acceptance'. This means the article will be published as long as the authors follow their preregistered data collection and analysis plan [@chambers_instead_2014; @nosek_registered_2014]. The population of Registered Reports in psychology is still relatively small (91 Registered Reports had been published as of February 22, 2018), which makes it possible to examine it in full.

The novelty of Registered Reports may attract early adopters who are also exploring other novel developments aimed at improving research practices in psychology, such as data and code sharing. We assumed that researchers who publish Registered Reports would also be likely to share data and code in public repositories, and to embrace computational reproducibility. In line with our assumptions, `r sum(all_data$availability, na.rm = TRUE)` out of `r length(all_data$doi)` articles in our final dataset shared data and code (`r round(100*sum(all_data$availability, na.rm = TRUE)/length(all_data$doi),1)`%). In comparison, after the journal *Cognition* introduced a mandatory data sharing policy, 136 out of 174 articles (78.2%) had a data availability statement, 85 of 174 articles (49%) had reusable data, and only 18 out of 174 articles (10.3%) provided the analysis code (Hardwicke et al., 2018). To evaluate the reproducibility of findings published in Registered Reports, we examined if data could be located, were available at the indicated location, could be opened in open-source software, were documented well enough to be understandable, and could be used to reproduce the main analyses reported in the published manuscript.

@@

Our main objective was to examine how reusable data and code underlying Registered Reports are, based purely on the information provided in the published literature. We examined how many authors voluntarily shared data and code, and the extent to which we could reproduce reported analyses without contacting the original authors. While reproducing the results reported in Registered Reports, we kept track of factors that facilitated reproducibility or that made reproducing the result more difficult. We report these qualitative findings with an aim to highlight how current practices can be improved.

@@

To find Registered Reports published in psychology we drew from a database of registered reports maintained by by Center for Open Science.^[https://www.zotero.org/groups/479248/osf/items/collectionKey/KEJP68G9] At the start of this project (06-05-2018) this database consisted of 118 published Registered Reports. Eighty-one articles in this database were published in the psychological literature. We limited our analysis to studies performed by single groups, since such articles are most representative of the researchers currently work, and excluded 7 large scale collaborations where dedicated team members were responsible for making the analysis reproducible, such as Registered Replication Reports [@hagger_multilab_2016] and Many Labs projects [@klein_investigating_2014; @klein_many_2018]. Upon further inspection of the 72 papers left in the dataset, it turned out that 10 were not formally Registered Reports. This left `r length(all_data$doi)` studies in our sample. When evaluating whether we could reproduce the original results, we limited ourselves to statistical software packages that we had experience with (R, SPSS, and JASP) and excluded studies that required expertise in software packages we are not trained in (e.g., dedicated EEG software, Python, Matlab), which led to the exclusion of `r sum(all_data$included_language == FALSE, na.rm = TRUE)` additional studies.

@@

We set out to reproduce the `r length(all_data$doi)` papers that met our inclusion criteria. For each article we coded whether the data and code were (a) linked, (b) available, (c) not software-specific, (d) understandable, and (e) reproducible. These five categories were inspired by FAIR data principles [@wilkinson_fair_2016] that address the findability, accessibility, interoperability, and reusability of data and code, but we did not explicitly code whether papers adhered to the exact definitions of the four FAIR principles. Our main aim was to examine the reproducibility of results, while adhering to FAIR criteria requires meeting more stringent requirements, for example concerning the presence of meta-data (which is missing for practically all datasets). We considered data and code to be linked when the manuscript included a unique link to the data and scripts. Ideally, such a link consists of a stable digital object identifier (DOI). A hyperlink to a website that contains the data and script also suffices, although normal hyperlinks are known to break over time [@gertler_reference_2017].

Of the `r length(all_data$doi)` papers, `r sum(all_data$linked)` linked to data and/or code in the article. Linking to data does not mean the data is actually available, and not linking to data in an article does not mean data is unavailable. For one article the link no longer worked (highlighting the need to use a stable DOI when linking to data). For three articles the link still worked, but there was no data at the linked destination. For three articles where there was no link to the data in the article, we were nevertheless able to find data on the Open Science Framework when searching for the title of the paper. For one paper the data was linked but not available, as the data was embargoed until a future date. Altogether, data was available for `r sum(all_data$availability)` out of `r length(all_data$doi)` papers.

We also coded the extent to which data and code was specific to software that was not freely available. When open source software is used, the analyses can be reproduced by anyone with a computer and internet, regardless of whether they have bought the same software package. When proprietary software is used, results might still be reproducible by anyone, but it could require more effort to do so. For example, SPSS produces proprietary .sav and .sps files. However, .sav files can be opened in R, and .sps files can be opened by a text editor and the code can be rewritten, as long the code is annotated well enough to be recoded into R. Note that we had access to SPSS and therefore reproduced the analyses using the original .sps scripts where available. The data files of one article where an EEG study was reported consisted of .eeg, .vhdr, and vmrk files that were analyzed in matlab, which we could not reproduce using open source software. This left `r sum(all_data$not_software_specific, na.rm = TRUE)` papers where data was available in a non-software-specific format.

@@

\caption{Of all articles in the Registered Report database 79 were psychology related, and `r length(all_data$doi)` were registered reports not part of a multi-lab Registered Replication Report. Of these `r length(all_data$doi)` papers, `r sum(all_data$linked)` linked to the data. After searching the OSF, data was available for `r sum(all_data$availability)` studies. Of these datasets, `r sum(all_data$understandable, na.rm = TRUE)` were documented well enough, for example through a codebook, so that variables were understandable. Of the `r length(all_data$doi)` papers `r sum(all_data$analysis_script_included, na.rm = TRUE)` shared the analysis script and data, for which `r spss_or_r_or_jasp` were in SPSS, R or JASP. Of these, the analysis script could be run for `r sum(all_data$run_script_final, na.rm = TRUE)`, of which `r sum(all_data$reproducible_final, na.rm = TRUE)` reproduced all main results. 
}

@@

One of the reasons to share data is allow other researchers to reproduce the reported results. Another important reason to share data is to enable other researchers to reuse the data. If the data can be understood by others, they can be used to answer novel research questions. This is one of the reasons why it is recommended to describe the dataset variables in a codebook. If the variables are not clearly described (e.g., the dataset consists of variables identified by abbreviations that only make sense to the original researcher), other researchers will not be able to reuse the data to answer novel questions. In our analyses, data were scored as 'understandable' when all variables were clearly named (e.g., 'Condition') and the values for variables were labeled (e.g., 0 = control, 1 = experimental). Out of the `r sum(all_data$not_software_specific, na.rm = TRUE)` papers with available data in a format that was not software specific, only `r sum(all_data$understandable, na.rm = TRUE)` datasets were described in enough detail to be understandable. This highlights the importance of adding a codebook with a datafile. For an explanation of how to create machine-readable codebooks (which was also used to create the codebook that is part of this manuscript) see @arslan_how_2019.

Finally, we examined how many of the `r sum(all_data$not_software_specific, na.rm = TRUE)` non-software-specific papers could be reproduced. It is possible that running the code on the data reproduces all analyses, even when the data file itself is not understandable (i.e., the data columns are not labeled). Two authors coded SPSS, R, and JASP analyses regarding (a) the executability of the script, and (b) the reproducibility of the results. After the initial coding, inter-rater reliability was low (`r round(agree(cbind(all_data$run_script_po == FALSE, all_data$run_script_jg == FALSE))$value,0)`% agreement on executability, and `r round(agree(cbind(all_data$reproducible_po == FALSE, all_data$reproducible_jg == FALSE))$value,0)`% agreement on reproducibility for SPSS scripts, `r round(agree(cbind(all_data$run_script_po == FALSE, all_data$run_script_nc == FALSE))$value,0)`% agreement on executability, and `r round(agree(cbind(all_data$reproducible_po == FALSE, all_data$reproducible_nc == FALSE))$value,0)`% agreement on reproducibility for R scripts). This initial low agreement provided two important insights about the definition of reproducibility and executability on the one hand, and the role of expertise on the other hand.

We used a dichotomous coding scheme to when coding whether the script could be executed whether the results could be reproduced ('yes' or 'no'), but coders often reported 'partial' reproducibility. Code often needed minor adjustments to run on the data, such as changing file locations, or loading packages in R, and coders sometimes took different approaches to how much they would adjust the code to make it run on the data. Furthermore, coders initially used different thresholds of reproducibility, based on whether every single result reported in a paper could be reproduced by the code and data, or only the main results reported in the article. After evaluating our initial coding round, we considered an article was reproducible when we could get the same *main results* as represented in the paper with at best *minor changes* to the analysis scripts. This means we considered the analysis reproducible, even if variables could only be found with reasonable effort or by making assumptions about how variable names mapped onto variables reported in the data analysis. Furthermore, we changed folder locations when needed and loaded libraries that were required. Finally, even though sometimes figures were generated in R and contained relevant information (e.g., the pattern of means) we did not require all figures to be reproducible.

@@

All authors have collectively discussed disagreements, which on several occasions led to clarifying ambiguities in rating strategies and correcting mistakes in the process of paper analysis (e.g. overlooked script files). The final ratings presented here have been discussed and approved by all authors, but will not be completely flawless, and we expect different teams of coders to reach slightly different conclusions (i.e., perfect reliability would be extremely difficult to achieve). It should be noted that the main goal of our analysis is to evaluate where there is room for improvement, and identify practices that researchers can use to make there work more reproducible.

For each article two coders examined whether the code could be run on the data. Of the original `r length(all_data$doi)` articles, `r sum(all_data$included_language == FALSE, na.rm = TRUE, na.rm = TRUE)` used Matlab and Python and were excluded from the analysis due to a lack of expertise in our team with these languages. In total code and data were available for `r sum(all_data$analysis_script_included ==TRUE & all_data$availability == TRUE, na.rm = TRUE)` articles, of which `r sum(all_data$analysis_script_included ==TRUE & all_data$availability == TRUE & all_data$included_language ==TRUE, na.rm = TRUE)` used R, SPSS, or JASP. We were able to run the code for `r sum(all_data$run_script_final == TRUE, na.rm = TRUE)` out of the `r sum(all_data$analysis_script_included ==TRUE & all_data$availability == TRUE & all_data$included_language ==TRUE, na.rm = TRUE)` articles that used SPSS, R, and JASP. R was used as a coding language in `r length(run_script_r)`, of which `r sum(run_script_r)` scripts could be run on the data, `r length(run_script_spss)` papers used SPSS, for `r sum(run_script_spss)` of which the script could be run, and `r length(run_script_r_spss)` papers used both SPSS and R, for which the scripts could be run for all `r sum(run_script_r_spss)` papers. JASP does not seperate the data and code, but instead stores both in a single JASP file. This means that the analyses are always directly linked to the code for every output. It is always clear which settings were used to generate results. Because of this useful feature, the `r sum(run_script_jasp)` articles that relied on JASP for the analyses always allowed us to reproduce the analyses.

@@

We analyzed data and scripts of `r length(all_data$doi)` Registered Reports to examine how many authors shared their data and code, and how often main results reported in the manuscript could be reproduced. In total, `r sum(all_data$analysis_script_included ==TRUE & all_data$availability == TRUE, na.rm = TRUE)` out of `r length(all_data$doi)` (or `r round(100*sum(all_data$analysis_script_included ==TRUE & all_data$availability == TRUE, na.rm = TRUE)/length(all_data$doi),1)`%) of the articles shared the underlying data and the code that was used to generate the results. Of the papers that shared both the data and the analysis code and used software we had experience with, we could reproduce the main results for `r round(100*sum(all_data$reproducible_final, na.rm = TRUE)/sum(all_data$analysis_script_included ==TRUE & all_data$availability == TRUE & all_data$included_language ==TRUE, na.rm = TRUE),1)`% of the papers. Authors of Registered Reports in psychology seem to voluntarily choose to share data and code relatively often compared to authors of articles in political science [@stockemer_data_2018]. Compared to authors of non-registered reports in psychology, voluntary data and code sharing is also relatively high, as is the reproducibility rate (taking into account that we reproduced articles without contacting the original authors). The reproducibility rate was higher than the 31% rate observed by Hardwicke et al. (2018), and both voluntary data sharing as reproducibility were higher than in the sample of papers from the journal *Science* in 2011-2012 analyzed in @stodden_empirical_2018.

Nevertheless, the reproducibility rate for articles where data and code were available show there is clear room for improvement in how reproducible published Registered Reports are, when we attempted to reproduce main analyses without contacting the authors. One of the main goals of our project was to identify ways to improve the reproducibility of published articles. We encountered several common issues that made results reported in Registered Reports difficult to reproduce (cf. Hardwicke et al., 2018). This leads to 4 points researchers in psychology should focus on to improve reproducibility, namely (a) add a codebook to data files, (b) annotate code so it is clear what the code does, and clearly structure code (e.g., using a README) so others know which output anaysis code creates, (c) list packages that are required in R and the versions used at the top of your R file, (d) check whether the code you shared still reproduces all analyses after revisions during the peer review process. We will discuss each of these points below, and link to examples of good practices that we encountered.

@@

Second, code should be well-annotated, so that it is understandable for researchers who did not write the code. Well-annotated code makes clear what the analysis code does, in which order it should be run, and which output each section of analysis code generates. A good example of well-annotated code can be found in the materials of @weston_role_2018. It helps to make clear how the analysis code relates to the analyses reported in the paper, to make it easier for others to identify which code generates which results in the paper. For one manuscript which was coded as not reproducible, there was too much unstructured code, and each analyses took too long to run, so that it was decided that the manuscript was not reproducible with a reasonable amount of effort mainly due to the lack of a clear indication which code needed to be run to reproduce specific results. Explicitly linking code in the analysis script to the final manuscript also helps researchers to check whether all results in the article are reproduced by the shared code. An example of a data analysis file that clearly links the code to the final articles can be found in the materials of @voorspoels_can_2014. If analyses are performed that are not included in the manuscript, this should be stated explicitly (e.g., assumption checks, exploratory analyses, etc.). The structure of analysis scripts can often be improved by creating different sections in the code, or creating different files for different parts of the data analysis (e.g., data cleaning, data preparation, exploratory data analysis, and confirmatory data analysis scripts). Third, it is highly recommended to perform a final check after the peer-review process has been completed to make sure any changes in the code introduced during the peer-review process are reflected in the shared data and code.

@@

While trying to reproduce the results of SPSS scripts, the biggest issue was the often confusing and unclear structure of the scripts. Large portion of the scripts were not annotated, and it was unclear which results they should produce. Often, the descriptive, confirmatory and exploratory analyses were not easily distinguishable because of an overall lack of structure. The absence of understandable variable and value labels in more than half of all SPSS scripts hindered our attempts to reproduce these results. Often the only time-efficient way to check if an article was reproducible so was to run the whole script, and search try to identify specific *p*-values or effect sizes from the article in the SPSS output. SPSS users should take greater care to clearly organize their analysis scripts by adding comments or a README file that links results generated by the SPSS script to the analyses reported in the manuscript. Another frequent problem consisted of missing or incorrectly labeled variables in the dataset, so the script could not run properly. We expect this is the result of authors updating or modifying either their datasets or their scripts during the publication process. This issue could be easily detected if a second author of the manuscript attempted to reproduce the analyses reported in the final manuscript before the data and scripts are shared publicly.
